Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating and Growing

### 2017-09-20 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/ContinuousGeneralisation_Paper_Sigspatial.tex
explained in a figure what a bay is, and what is the width of the bay

\usepackage{booktabs} % For formal tables
\usepackage{xspace}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
\usepackage{gensymb}  % for degree sign, e.g., temperature

@@

\begin{document}
\title{Continuous Generalization of Buildings \\ by Growing and Aggregating}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

\begin{abstract}
To enable smooth zooming, we propose a method to continuously 
generalize buildings from a given start map to a smaller-scale goal map, where 
there are only built-up area polygons instead of individual building polygons.
We name the buildings on the start map \emph{original buildings}.
%
For an intermediate scale, 
we aggregate the original buildings that will become too close 
by adding bridges.
We grow (bridge) original buildings based on buffering 
and simplify the grown buildings.
We take into account the shapes of the buildings 
both at the previous map and goal map to make sure that 
the buildings are always growing.
%
\newline\indent
The advantages of our method are as follows. 
First, the buildings grow continuously 
and, at the same time, are simplified.
Second, right angles of buildings are preserved during growing: the merged 
buildings still look like buildings. 
Third, the distances between buildings are 
always larger than a specified threshold.
We do a case study to show the performances of our method.
\end{abstract}

>>>>

\usepackage{booktabs} % For formal tables
\usepackage{xspace}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{tikz,pgfplots}
\pgfplotsset{compat=1.3} %make y lable compact in a tikz picture with axes

@@

\begin{document}
\title{Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating 
and Growing}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

@@

\begin{abstract}
To enable smooth zooming, we propose a method to continuously 
generalize buildings from a given start map to a smaller-scale goal map, where 
there are only built-up area polygons instead of individual building polygons.
We name the buildings on the start map \emph{original buildings}.
%
For an intermediate scale, 
we aggregate the original buildings that will become too close 
by adding bridges.
We grow (bridge) original buildings based on buffering, 
and we also simplify the grown buildings.
We take into account the shapes of the buildings 
both at the previous map and goal map to make sure that 
the buildings are always growing.
%
\newline\indent
The advantages of our method are as follows. 
First, the buildings grow continuously 
and, at the same time, are simplified.
Second, right angles of buildings are preserved during growing: the merged 
buildings still look like buildings. 
Third, the distances between buildings are 
always larger than a specified threshold.
We do a case study to show the performances of our method.
\end{abstract}

### 2017-09-20 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
explained in a figure what a bay is, and what is the width of the bay

Our contributions are as follows.
In \sect\ref{sec:Methodology},
we continuously generalize a start map, of buildings, 
to a smaller-scale goal map.
The generalization consists of aggregating, growing, and simplifying.
We aggregate original buildings which will be too close at an output scale 
by introducing bridges.
We grow (bridged) original buildings by buffering,
where we use so-called \emph{miter} joins to keep the right angles of buildings.
Because of using this kind of joins instead of \emph{round} ones,
we have more problems.
We show how to solve these problems.
We also simplify the buildings at the output scale.
We carry out a case study 
and discuss the performances of our method in \sect\ref{sec:CaseStudy}.
We conclude our paper in \sect\ref{sec:Conclusion}.

@@

The continuous generalization is carried by dilating the original buildings. 
When dilated buildings become too close at time $t$
and we aggregate them by introducing bridges.
We grow the (bridged) original buildings by buffering with miter joins.
At each time, the grown buildings need to be simplified to look like buildings 
and this simplification is carried out in two steps:
the first one is to use dilation and erosion 
to remove ``dents'' and ``bumps''; 
the second step is to remove vertices using Imai--Iri algorithm.
To make sure that buildings never shrink when $t$ is increasing,
for a building, we merge its shape at time $t$ 
and its shape at the immediately previous step (before $t$). 
Also, we clip the building using the shape on goal map to ensure some 
continuity.

@@

\subsection{Simplifying grown buildings based on dilation and erosion}
\label{sec:DilationErosion}
As mentioned earlier, building simplification methods have already been 
proposed. \citet{Damen2008} generalized buildings using morphological operators.
A drawback of this method is that the orientation of the buildings have to be 
identified.
\citet{Meijers2016} simplified buildings 
based on offset curves generated from straight skeletons.
Our method is similar to \citet{Meijers2016}.
Our proposition is to dilate and erode the buildings, to remove dents and 
bumps that can occur when buildings grow.
(see \fig\ref{fig:RemoveDentAndBump}).
The operations of dilation and erosion are available from library 
\textsc{Clipper} \citep{Johnson2014}.

@@

We wish to remove ``bays'' 
which have ``widths'' less than $2 r_\mathrm{h}$. 
Variable $r_\mathrm{h}= 2\sqrt{a_\mathrm{h}/\pi}$
is the radius of a hole which is just large enough to be presented on map.
Following \citep{Chaudhry2008}, we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ 
on map.
Sometimes, our $\dtrm{D}$ is not large enough to do so 
because of the limitation from \eq\ref{eq:d_DtBound}.
We define
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} =\min (\frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}, r_\mathrm{h} M_t) .
\end{equation}

\todo{please explain in a figure what a bay is, and what is the width of the 
bay}

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Aggregating original buildings in the same group by introducing 
		bridges.
		Then grow the bridged buildings.}
	\label{fig:GrowAndBridge}
\end{figure*}

@@

Our program took $93.6\,\mathrm{s}$ 
to compute the goal shapes of the built-up areas.
\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
In \fig\ref{fig:GoalShape}b,
the $56$ built-up areas have $2{,}095$ edges before line simplification.
Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
In comparison, there are $1{,}597$ edges left if we simplify using
the Douglas--Peucker algorithm.

\begin{figure}[tb]
	\centering
	\includegraphics{Data}
	\caption{Data.
		There are $2{,}590$ buildings, 
		which in total have $19{,}255$ edges and have area
		$448{,}996.8\,\mathrm{mm}^2$.}
	\label{fig:Data}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	width= \linewidth-0.1cm,
	axis lines = left,
	%	axis x line=center,
	%	axis y line=left,
	xtick={0.1,0.2,...,1},
	ytick={500,1000,...,3000},
	xlabel={$t$},
	ylabel={number of buildings},
	xlabel style={below right},
	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
	xlabel style={at={(axis description cs:1,0)},anchor=north},
	%	ylabel style={above left},
	xmin=0,
	xmax=1.1,
	ymin=0,
	ymax=3200,
	cycle list name=black white,
	]
	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
	\addplot+  coordinates {
		(0,2590)
		(0.1,1963)
		(0.2,758)
		(0.3,304)
		(0.4,177)
		(0.5,122)
		(0.6,92)
		(0.7,73)
		(0.8,66)
		(0.9,59)
		(1,56)		
	};
	\legend{\quad radical law, \quad our results}
	\end{axis}
	\end{tikzpicture}
	\caption{A comparison of the numbers of building between our results and 
		T\"opfer's radical law.}
	\label{fig:BuilidngNumber}
\end{figure}

@@

%Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{mm}^2$.

>>>>

Our contributions are as follows.
In \sect\ref{sec:Methodology},
we continuously generalize a start map, of buildings, 
to a smaller-scale goal map.
The generalization consists of aggregating, growing, and simplifying.
We aggregate original buildings which will be too close at an output scale 
by adding bridges.
We grow (bridged) original buildings by buffering,
where we use so-called \emph{miter} joins to keep the right angles of buildings.
Because of using this kind of joins instead of \emph{round} ones,
we have more problems.
We show how to solve these problems.
We also simplify the buildings at the output scale.
We carry out a case study 
and discuss the performances of our method in \sect\ref{sec:CaseStudy}.
We conclude our paper in \sect\ref{sec:Conclusion}.

@@

The continuous generalization is carried by dilating the original buildings. 
When dilated buildings become too close at time $t$
and we aggregate them by adding bridges.
We grow the (bridged) original buildings by buffering with miter joins.
At each time, the grown buildings need to be simplified to look like buildings 
and this simplification is carried out in two steps:
the first one is to use dilation and erosion 
to remove ``dents'' and ``bumps''; 
the second step is to remove vertices using Imai--Iri algorithm.
To make sure that buildings never shrink when $t$ is increasing,
for a building, we merge its shape at time $t$ 
and its shape at the immediately previous step (before $t$). 
Also, we clip the building using the shape on goal map to ensure some 
continuity.

@@

\subsection{Simplifying grown buildings based on dilation and erosion}
\label{sec:DilationErosion}
As mentioned earlier, building simplification methods have already been 
proposed. \citet{Damen2008} generalized buildings using morphological operators.
A drawback of this method is that the orientation of the buildings have to be 
identified.
\citet{Meijers2016} simplified buildings 
based on offset curves generated from straight skeletons.
Our method is similar to \citet{Meijers2016}.
Our proposition is to dilate and erode the buildings, to remove dents and 
bumps that can occur when buildings grow
(see \fig\ref{fig:RemoveDentAndBump}).

@@

A ``bay'' may appear when we grow a bridged building
(see \fig\ref{fig:RemoveBay}b).
We remove such a bay by dilating (see \fig\ref{fig:RemoveBay}c)
and then eroding (see \fig\ref{fig:RemoveBay}d) with distance $\dtrm{D}$.
We define the width of a bay as the diameter of the largest circle 
that can be placed in the bay.
If the width of a bay is smaller than $2\dtrm{D}$, 
then the bay can be removed by dilating and eroding with distance $\dtrm{D}$.
We wish to remove bays 
which have widths less than $2 r_\mathrm{h}$.
Variable $r_\mathrm{h}= 2\sqrt{a_\mathrm{h}/\pi}$
is the radius of a hole 
which is just large enough to be presented on map.
Following \citep{Chaudhry2008}, 
we set area $a_\mathrm{h} = 8\,\mathrm{mm}^2$ on map.
Sometimes, our $\dtrm{D}$ is not large enough to do so 
because of the limitation from \eq\ref{eq:d_DtBound}.
We define
\begin{equation}
\label{eq:d_Dt}
\dtrm{D} =\min (\frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}, r_\mathrm{h} M_t) .
\end{equation}

\begin{figure}[tb]
	\centering
	\includegraphics[]{RemoveBay}
	\caption{Removing a bay by dilating and eroding.
		(a) An aggregated building by adding bridges 
		(see \sect\ref{sec:Aggregate}).
		(b) Growing the aggregated building with distance~$\dtrm{G}$,
		where the marked a region is a bay.
		(c) Dilating the grown building with~$\dtrm{D}$.
		(d) Eroding the dilated building with~$\dtrm{D}$.
	}
	\label{fig:RemoveBay}
\end{figure}

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Aggregating original buildings in the same group by adding 
		bridges.
		Then grow the bridged buildings.}
	\label{fig:GrowAndBridge}
\end{figure*}

@@

Our program took $93.6\,\mathrm{s}$ 
to compute the goal shapes of the built-up areas.
\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
The $56$ built-up areas have $2{,}095$ edges before line simplification.
Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
In comparison, there are $1{,}597$ edges left if we simplify using
the Douglas--Peucker algorithm.

\begin{figure}[tb]
	\centering
	\includegraphics{Data}
	\caption{Data.
		There are $2{,}590$ buildings, 
		which in total have $19{,}255$ edges and have area
		$448{,}996.8\,\mathrm{m}^2$.}
	\label{fig:Data}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	height=5cm,
	width= \linewidth-0.1cm,
	axis lines = left,
	%	axis x line=center,
	%	axis y line=left,
	xtick={0.1,0.2,...,1},
	ytick={500,1000,...,3000},
	xlabel={$t$},
	ylabel={number of buildings},
	xlabel style={below right},
	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
	xlabel style={at={(axis description cs:1,0)},anchor=north},
	%	ylabel style={above left},
	xmin=0,
	xmax=1.1,
	ymin=0,
	ymax=3200,
	cycle list name=black white,
	]
	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
	\addplot+  coordinates {
		(0,2590)
		(0.1,1963)
		(0.2,758)
		(0.3,304)
		(0.4,177)
		(0.5,122)
		(0.6,92)
		(0.7,73)
		(0.8,66)
		(0.9,59)
		(1,56)		
	};
	\legend{\quad radical law, \quad our results}
	\end{axis}
	\end{tikzpicture}
	\caption{A comparison of the numbers of building between our results and 
		T\"opfer's radical law.}
	\label{fig:BuilidngNumber}
\end{figure}

@@

%Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{m}^2$.
